%This is our Abstract
\begin{abstract}
    Consumer lawn mowers available for purchase all are burdened by their high starting investment cost, unexpected costs of maintenance, as well as being difficult to use on rough uneven terrain. The objective of this project is to design and construct an autonomous robotic lawn mower that will utilize an internal system to detect the boundaries of the yard, and mow the lawn at consistent levels, regardless of terrain. Autonomous Vehicles are on a rise due to Artificial Intelligence models currently training on real-world datasets. These systems can also translate to an autonomous system for lawn mowing as well, using user inputted data to act precisely. This project intends to develop a high powered lawn mower for a fraction of the cost. Through the use of radar and different proximity sensors located around the robot, the project will be controlled via an automated ground station software that will run as needed as well as an option to be remotely operated. The robot will be given either a set of instructions by the user to perform its task or be given a predefined setting and execute that function using machine learning modeling handled by the microcontroller. In addition, the lawn mower will be lightweight and portable in order to improve efficiency and decrease potential labor costs. The overall intention of this project is to create an autonomous lawn mower within a constrained budget of \$500 and analyze the benefits and constraints of its usage compared to consumer models.  
\end{abstract}