%Introduction Paragraph to Chapter
%LawnBot is an affordable automated lawnmower that is designed for your average homeowner. With a budget of \$500 we plan on competing with other automated lawnmowers that go for anywhere from \$900 - \$2000. We plan to compete with them by using cheaper exterior materials instead of metals but also using reliable hardware with equally as reliable software. The LawnBot will be setup with a controller that the user controls to control the robot so it records the data on where the user wants the LawnBot to cut the grass. This lawnmower will have different sensors to detect different items in front of it so it can avoid them. This project is aimed to have an affordable automated lawnmower that helps anyone who could be to busy or does not have the capabilities to cut their own grass. \par

\subsection{Weekly Overall Status}
Our team is waiting for the materials list to be ordered by UB and has a general outline for what we want to accomplish and a estimated time line for once the materials arrive. We expect a bit of a rush to meet our January 15th deadline for ASEE but have confidence that we will be able to reach our goals and have enough information to provide on the draft paper. We also need to discuss with the university what is expected in terms of fee coverage for the ASEE conference. During these next two weeks, we will revise our abstract as well as begin planning out the draft paper needed to submit for ASEE. We also will finalize our algorithm for mapping and pathing. Our design team is limited in tasks due to lack of materials. \par

\subsection{Challenges}
Some challenges we are facing is that it will be difficult to make any progress on the machine until we have our equipment. Another challenge is working out the algorithm we plan to use in terms of Mapping and in terms of pathing. We want to make sure that both algorithms that will serve our project will be sufficient in our goals. We are hopeful that our materials will arrive soon after winter break in order to meet our deadlines necessary for ASEE.
%Some issues our group is currently are the design and load distribution. After meeting with Dr.Patel, he brought up concerns over our amperage used in our current sketch. Our current design draws approximately 10 Amperes between our current fan choice and the other components. Our fan is currently drawing the most power at approximately 6.6 Amperes, which will take nearly a third of our battery within an hour by itself. Our group is currently recalculating the our power draws to make sure everything is correct. \par

%With our load distribution, we are looking into how to support the 12 Volt 15 Amp-hour battery we have purchased. The battery is currently comes in at 6.5 pounds and we will need to plan our unit around this. We also need to make sure that our motors and wheels will be able to support this weight without compromising the integrity of the unit. \par